Interest Flooding Attack and Countermeasures in Named Data Networking

### 2013-01-15 02-ndn-background.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@932 df1a90cd-247b-4364-bdaf-287a704eb499

To retrieve data, a consumer requests it by sending an Interest packet with the name of the desired content in it.
Routers use this name to route the Interest towards data sources, and a Data packet whose name matches the name in the Interest is returned to the consumer by following the reverse path of the Interest. Similar to IP, Interest forwarding is based on longest name prefix match, but, unlike IP, an Interest packet and its matching Data packet always take symmetric path.
%% An Interest is ``satisfied'' when it is matched with a Data packet.

Each NDN router maintains three major data structures:
\begin{itemize}
\item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards data producers. Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicates the same Interest is forwarded along multiple paths.
\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, defining allowed %(multipath)
 directions to where Interests can be forwarded. 
% Having one-to-many relationship in this table allows multipath forwarding of Interests.}
\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this node, allowing efficient data retrieval by different consumers.
\end{itemize}

When a router receives an Interest packet, it first checks whether there is a matching data in its CS.
If a match is found, the Data packet is sent back to the incoming interface of the Interest packet.
If not, the Interest name is checked against the entries in the PIT. 
If the name already exists in the PIT, then it can be a duplicate Interest (identified by a random number each Interest carries) that should be dropped,
or an Interest from another consumer asking for the same Data, which requires the incoming interface of this Interest to be added to the existing PIT entry.
If the name does not exist in the PIT, the Interest is added into the PIT and forwarded to the interface chosen by the strategy module, which uses FIB as input for its decision.

>>>>

To retrieve data, a consumer requests it by sending an Interest packet with the name of the desired content in it.
Routers use this name to route the Interest towards data sources, and a Data packet whose name matches the name in the Interest is returned to the consumer by following the reverse path of the Interest. Similar to IP, Interest forwarding is based on longest name prefix match, but, unlike IP, an Interest packet and its matching Data packet always take symmetric paths.
%% An Interest is ``satisfied'' when it is matched with a Data packet.

Each NDN router maintains three major data structures:
\begin{itemize}
\item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards data sources. Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicates the same Interest is forwarded along multiple paths.
\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, defining allowed %(multipath)
 directions to where Interests can be forwarded. 
% Having one-to-many relationship in this table allows multipath forwarding of Interests.}
\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this node, allowing efficient data retrieval by different consumers.
\end{itemize}

When a router receives an Interest packet, it first checks whether there is a matching data in its CS.
If a match is found, the Data packet is sent back to the incoming interface of the Interest packet.
If not, the Interest name is checked against the entries in the PIT. 
If the name already exists in the PIT, then it can be a duplicate Interest (identified by a random number each Interest carries) that should be dropped,
or an Interest from another consumer asking for the same Data, which requires the incoming interface of this Interest to be added to the existing PIT entry.
If the name does not exist in the PIT, the Interest is added into the PIT and forwarded to the interface chosen by the strategy module, which uses FIB as input for its decisions.

### 2013-01-15 03-interest-flooding.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@932 df1a90cd-247b-4364-bdaf-287a704eb499

As we explained earlier, Interest packets in NDN are routed through the network based on their content name prefixes and consume memory resources at intermediate routers. Thus they can be used to launch DDoS attacks in an NDN network. An attacker or a set of distributed attackers can inject excessive amounts of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}). 
%%% Alex %%% We have (almost) exactly the same sentence in the intro. I think here is kind of redundant, as it is obvious how we call the attack from the section title.  Also, we are referring to the term again in the last paragraph of the section.
% We coin the term \emph{Interest flooding} to refer to these network-level flooding attacks.

@@

Since an NDN network fetches name data, an adversary cannot target specific routers or end-hosts.
%% as neither is required to have a globally routable network identity/address.
However, an adversary can target a specific namespace.
For example in Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{/foo/bar} prefix to make them effective. It also assumes the producer is single-homed and the data is not replicated elsewhere. With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding}.}
A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.

@@

An effective Interest flooding attack is non-trivial to create.
To target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
%In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and 
To avoid an Interest being served from caches of intermediate routers, every single malicious Interest has to request an unpopular or non-existing content, e.g., content with a unique name (\emph{unique junk Interests}). In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network. Other less effective strains of Interest flooding attacks can be mitigated by applying the same or similar countermeasures.

>>>>

As we explained earlier, Interest packets in NDN are routed through the network based on their content name prefixes and consume memory resources at intermediate routers. This makes them a potential tool to launch DDoS attacks in an NDN network. An attacker or a set of distributed attackers can inject excessive amounts of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}). 
%%% Alex %%% We have (almost) exactly the same sentence in the intro. I think here is kind of redundant, as it is obvious how we call the attack from the section title.  Also, we are referring to the term again in the last paragraph of the section.
% We coin the term \emph{Interest flooding} to refer to these network-level flooding attacks.

@@

Since an NDN network fetches data by its name, an adversary cannot target specific routers or end-hosts.
%% as neither is required to have a globally routable network identity/address.
However, an adversary can target a specific namespace.
For example in Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{/foo/bar} prefix to make them effective. It also assumes the producer is single-homed and the data is not replicated elsewhere. With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding}.}
A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.

@@

An effective Interest flooding attack is non-trivial to create.
To target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
%In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and 
To avoid an Interest being served from caches of intermediate routers, every single malicious Interest has to request an unpopular or non-existing content, e.g., content with a unique name (\emph{unique junk Interests}). In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network. However, other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.

### 2013-01-15 paper.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@920 df1a90cd-247b-4364-bdaf-287a704eb499
Reverting back the old title. Update of email addresses
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@922 df1a90cd-247b-4364-bdaf-287a704eb499
Alex, you cannot copy UCI paper's title...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@925 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@932 df1a90cd-247b-4364-bdaf-287a704eb499

\title{Interest Flooding Attacks and Countermeasures in Named Data Networking}%:\\ Cache/Content Poisoning}

%I don't think submission is anonymous...
% I PUT AUTHOR NAMES IN ALPHEBETICAL ORDER. It is the common practice in security and I always list authors alphebetically in my publications. -Ersin 
\author{
    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
    \\\{alex, ilya, lixia\}@ucla.edu}
    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
}

@@

\begin{abstract}
Distributed Denial of Service attack is an ongoing problem in today's Internet, where packets from large numbers of compromised hosts thwart the paths to the victim site and/or overload the victim machines. 
In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network forwards Data packets upon request only, effectively eliminating many existing DDoS attacks. 
However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  
In this paper we investigate effective solutions to mitigate Interest flooding.
We show that NDN's inherent properties to keep per packet state on each router and flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
Our evaluation through simulations shows that the solution can quickly and effectively respond and mitigate Interest flooding.
\end{abstract}

>>>>

%\title{Mitigating Interest Flooding DDoS Attacks in NDN}

\title{Interest Flooding Attack and Countermeasures in Named Data Networking}%:\\ Cache/Content Poisoning}

%I don't think submission is anonymous...
% I PUT AUTHOR NAMES IN ALPHEBETICAL ORDER. It is the common practice in security and I always list authors alphebetically in my publications. -Ersin 
\author{
    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
    \\\{afanasev, iliamo, lixia\}@cs.ucla.edu}
    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
}

@@

\begin{abstract}
Distributed Denial of Service attack is an ongoing problem in today's Internet, where packets from large numbers of compromised hosts thwart the paths to the victim site and/or overload the victim machines. 
In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network delivers Data packets upon request only, effectively eliminating many existing DDoS attacks. 
However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  
In this paper we investigate effective solutions to mitigate Interest flooding.
We show that NDN's inherent properties to keep per packet state on each router and flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
Our evaluation through simulations shows that the solution can quickly and effectively respond and mitigate Interest flooding.
\end{abstract}
